### 2021-04-13 paper.Rmd
small changes, typos

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics, Monash University
    email: stuart.a.lee@monash.edu
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics, Monash University
    affiliation: Monash University
    email: dicook@monash.edu
  - name: Natalia Da Silva
    address: |
      | Instituto de Estadística (IESTA), Universidad de la República
    affiliation: Universidad de la República
    email: natalia@iesta.edu.uy
  - name: Ursula Laa 
    affiliation: University of Natural Resources and Life Sciences
    address:  |
      | Institute of Statistics, University of Natural Resources and Life Sciences
    email:  ursula.laa@boku.ac.at
  - name: Nicholas Spyrison
    address: |
      | Faculty of Information and Technology, Monash University
    affiliation: Monash University
    email: nicholas.spyrison@monash.edu
  - name: Earo Wang
    address: |
      | Department of Statistics, The University of Auckland
    affiliation: The University of Auckland
    email: earo.wang@auckland.ac.nz
  - name: H. Sherry Zhang
    address: |
      | Department of Econometrics and Business Statistics, Monash University
    affiliation: Monash University
    email: huize.zhang@monash.edu
title:
  formatted: "A Review of the State-of-the-Art on Tours for Dynamic Visualisation of High-dimensional Data"
abstract: > 
  This article discusses a high-dimensional visualization technique called the tour, which can be used to view data in more than three dimensions. We review the theory and history behind the technique, as well as modern software developments and applications of the tour that are being found across the sciences and machine learning. 
keywords:
  formatted: ["tours", "data visualization", "high-dimensional data", "data science", "exploratory data analysis"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

@@

Instead of randomly generating targets, guided tour [@Cook1995-ae] finds its targets with a technique called projection pursuit [@Friedman1974-ck].  In projection pursuit, an index function is defined that is a surjective mapping from the projection $Y$ in $\mathbb{R}^{n \times d}$ to a scalar in $\mathbb{R}$. The guided tour iteratively optimizes the index function in the projection pursuit and produces the most interesting projection according to the index measure. The right panel of Figure \ref{fig:notation-target-gen} shows an example of a guided tour path.

>>>>

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics, Monash University
    email: stuart.a.lee@monash.edu
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics, Monash University
    affiliation: Monash University
    email: dicook@monash.edu
  - name: Natalia da Silva
    address: |
      | Instituto de Estadística (IESTA), Universidad de la República
    affiliation: Universidad de la República
    email: natalia@iesta.edu.uy
  - name: Ursula Laa 
    affiliation: University of Natural Resources and Life Sciences
    address:  |
      | Institute of Statistics, University of Natural Resources and Life Sciences
    email:  ursula.laa@boku.ac.at
  - name: Nicholas Spyrison
    address: |
      | Faculty of Information and Technology, Monash University
    affiliation: Monash University
    email: nicholas.spyrison@monash.edu
  - name: Earo Wang
    address: |
      | Department of Statistics, The University of Auckland
    affiliation: The University of Auckland
    email: earo.wang@auckland.ac.nz
  - name: H. Sherry Zhang
    address: |
      | Department of Econometrics and Business Statistics, Monash University
    affiliation: Monash University
    email: huize.zhang@monash.edu
title:
  formatted: "A Review of the State-of-the-Art on Tours for Dynamic Visualisation of High-dimensional Data"
abstract: > 
  This article discusses a high-dimensional visualization technique called the tour, which can be used to view data in more than three dimensions. We review the theory and history behind the technique, as well as modern software developments and applications of the tour that are being found across the sciences and machine learning. 
keywords:
  formatted: ["tours", "data visualization", "high-dimensional data", "data science", "exploratory data analysis"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

@@

Instead of randomly generating targets, guided tour [@Cook1995-ae] finds its targets with a technique called projection pursuit [@Friedman1974-ck].  In projection pursuit, an index function is defined that is a subjective mapping from the projection $Y$ in $\mathbb{R}^{n \times d}$ to a scalar in $\mathbb{R}$. The guided tour iteratively optimizes the index function in the projection pursuit and produces the most interesting projection according to the index measure. The right panel of Figure \ref{fig:notation-target-gen} shows an example of a guided tour path.
